---
title: "lab_8"
author: "Cristina Mancilla and Charlie Wilson"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r}
library(tidyverse)
library(corrplot)
library(broom)
library(here)
library(modelsummary)
```

```{r}
## Read in slo_homes.csv

homes <- read_csv(here("slo_homes.csv"))

```


### Crate a subset with 4 cities 
Task: create a subset (called homes_subset) that only contains observations where the city is: 

- "San Luis Obispo" 
-"Atascadero"
-"Arroyo Grande"
-"Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

```{r}
homes_subset %>% 
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price), 
            sd_price = sd(Price), 
            mean_sqft = mean(SqFt))
  
```

## Explore the relationship between square footage and home price 

```{r}
  ggplot(data = homes_subset, aes(x = SqFt, y = Price)) + 
  geom_point() +
  geom_smooth(method = "lm")
```
# this is a positive linear relationship 

# Use multiple linear regression to investigate relationships between several predictor variables and home price. 

Create 2 different permutations of this model: 

(1) Price ~ City, Bedrooms, Bathrooms, SqFr, Status (lm1)
(2) Price ~ Ciry, SqFT, Status (lm2)
(3) Try another one (lm3)

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)
lm1

lm2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)
lm3 <- lm(Price ~ City + Bedrooms + SqFt, data = homes_subset)
```
# Use fct_relevel to specif a new reference level

```{r}

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))

# This will use SLO as the reference level for city 

lm_slo <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = new_homes_subset)

lm_slo
```
### Explore correlations between our quantitaive variables 
Task: make a subset called homes_quant (starting from home_subset) that only contains the variables from Price through SqFt 


```{r}
homes_quant <- homes_subset %>%
  select(Price:SqFt)
```


```{r}
homes_corr <- cor(homes_quant)
homes_corr
```


```{r}
corrplot(homes_cor, method = "eclipse")
```
```{r}
### Compare AIC values 

AIC(lm1)
AIC(lm2)
```

### Use modelsummary() to return multiple model outputs 

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### check out the diagnostic plots for lm1 

```{r}
plot(lm1)
```
# Use broom:: augment () to return the predictions for existing observations 

```{r}
home_predictions <- augment(lm1)
```

# make a histogram of the residuals from this model (lm1)

```{r}
ggplot(data = home_predictions, aes(x = .resid)) +
  geom_histogram()
```

